---
title: "Fitness depending on Selection Coeff 0.3"
author: "Ece Varol"
date: "7/2/2019"
output: html_document
---




```{r}
#Fitness Null
#Selection Coefficient=0.3
#Threshold= 4
#Recombination Rate 10^-8
rm(list=ls())
work_dir <- "~/Desktop/Research"
setwd(work_dir)

output<-read.delim("mutation5.txt", sep=" ", header=FALSE)
gen<- matrix(rep(0,40000),nrow=20000, ncol=2)

for (i in 1:20000) {
  gen[i,1]<-output[i,1]
  sum<-rowSums(output[i,2:500])
  gen[i,2]<- sum/500
}

thres=4
percent<- matrix(rep(0,20000*500),nrow=20000, ncol=500)

#People with >4 mutations=1
#People with <4 mutations= 0
for (i in 1:20000){
  percent[i,1]<-output[i,1]
  
  for(t in 2:500){
   if(output[i,t] >thres)
    percent[i,t]<-1
  else
    percent[i,t]<-0
  }
}

#Sum up the number of individuals that have more than threshold value of mutations per generation
percentnew<- matrix(rep(0,40000),nrow=20000, ncol=2)
 for(i in 1:20000){
   percentnew[i,1]<- percent[i,1]
   sums<-sum(percent[i,2:500])
   percentnew[i,2]<-sums
 }


#Plot Number of Mutations per Individual with Selection Coef=0.001
plot(gen[,1],gen[,2],xlab="Generation",ylab="Number of Mutations per Individual", type="l", xlim=c(0,20000), ylim=c(0,4))

#Plot the number of individuals that have mutations above the threshold vs.generation
plot(percentnew[,1],percentnew[,2]/500, type="l", xlab="Generation", ylab="% of Individuals with >4 Mutations", main="Disease Prevalance", col=c("red"), xlim=c(0,20000))

```

Show in New WindowClear OutputExpand/Collapse Output
Error: '\D' is an unrecognized escape in character string starting ""C:\D"
Modify Chunk OptionsRun All Chunks AboveRun Current Chunk
Show in New WindowClear OutputExpand/Collapse Output

The working directory was changed to /Users/ecevarol/Desktop/Research inside a notebook chunk. The working directory will be reset when the chunk is finished running. Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.
R Console


Control Group
```{r}
rm(list=ls())
#Fitness Null
#Selection Coefficient=0.3
#Threshold= 7
thres=7
work_dir <- "~/Desktop/Research"
setwd(work_dir)

output<-read.delim("mutation7.txt", sep=" ", header=FALSE)
gen<- matrix(rep(0,40000),nrow=20000, ncol=2)

for (i in 1:20000) {
  gen[i,1]<-output[i,1]
  sum<-rowSums(output[i,2:500])
  gen[i,2]<- sum/500
}


percent<- matrix(rep(0,20000*500),nrow=20000, ncol=500)

#People with >4 mutations=1
#People with <4 mutations= 0
for (i in 1:20000){
  percent[i,1]<-output[i,1]
  
  for(t in 2:500){
   if(output[i,t] >thres)
    percent[i,t]<-1
  else
    percent[i,t]<-0
  }
}

#Sum up the number of individuals that have more than threshold value of mutations per generation
percentnew<- matrix(rep(0,40000),nrow=20000, ncol=2)
 for(i in 1:20000){
   percentnew[i,1]<- percent[i,1]
   sums<-sum(percent[i,2:500])
   percentnew[i,2]<-sums
 }


#Plot Number of Mutations per Individual with Selection Coef=0.001
plot(gen[,1],gen[,2],xlab="Generation",ylab="Number of Mutations per Individual", type="l", xlim=c(0,20000), ylim=c(0,7))

#Plot the number of individuals that have mutations above the threshold vs.generation
plot(percentnew[,1],percentnew[,2]/500, type="l", xlab="Generation", ylab="% of Individuals with >7 Mutations", main="Disease Prevalance", col=c("red"), xlim=c(0,20000),ylim=c(0,1))
```


```{r}
rm(list=ls())
#Fitness Null
#Selection Coefficient=0.2
#Threshold= 7
#Recombination Rate 10^-8
thres=7
work_dir <- "~/Desktop/Research"
setwd(work_dir)

output<-read.delim("mutation8.txt", sep=" ", header=FALSE)
gen<- matrix(rep(0,40000),nrow=20000, ncol=2)

for (i in 1:20000) {
  gen[i,1]<-output[i,1]
  sum<-rowSums(output[i,2:500])
  gen[i,2]<- sum/500
}


percent<- matrix(rep(0,20000*500),nrow=20000, ncol=500)

#People with >4 mutations=1
#People with <4 mutations= 0
for (i in 1:20000){
  percent[i,1]<-output[i,1]
  
  for(t in 2:500){
   if(output[i,t] >thres)
    percent[i,t]<-1
  else
    percent[i,t]<-0
  }
}

#Sum up the number of individuals that have more than threshold value of mutations per generation
percentnew<- matrix(rep(0,40000),nrow=20000, ncol=2)
 for(i in 1:20000){
   percentnew[i,1]<- percent[i,1]
   sums<-sum(percent[i,2:500])
   percentnew[i,2]<-sums
 }


#Plot Number of Mutations per Individual with Selection Coef=0.001
plot(gen[,1],gen[,2],xlab="Generation",ylab="Number of Mutations per Individual", type="l", xlim=c(0,20000), ylim=c(0,thres))

#Plot the number of individuals that have mutations above the threshold vs.generation
plot(percentnew[,1],percentnew[,2]/500, type="l", xlab="Generation", ylab="% of Individuals with >7 Mutations", main="Disease Prevalance", col=c("red"), xlim=c(0,20000),ylim=c(0,1))
```

```{r}
rm(list=ls())
#Fitness Null
#Selection Coefficient=0.2
#Threshold= 4
#Recombination Rate 10^-8
thres=4
work_dir <- "~/Desktop/Research"
setwd(work_dir)

output<-read.delim("mutation9.txt", sep=" ", header=FALSE)
gen<- matrix(rep(0,40000),nrow=20000, ncol=2)

for (i in 1:20000) {
  gen[i,1]<-output[i,1]
  sum<-rowSums(output[i,2:500])
  gen[i,2]<- sum/500
}


percent<- matrix(rep(0,20000*500),nrow=20000, ncol=500)

#People with >4 mutations=1
#People with <4 mutations= 0
for (i in 1:20000){
  percent[i,1]<-output[i,1]
  
  for(t in 2:500){
   if(output[i,t] >thres)
    percent[i,t]<-1
  else
    percent[i,t]<-0
  }
}

#Sum up the number of individuals that have more than threshold value of mutations per generation
percentnew<- matrix(rep(0,40000),nrow=20000, ncol=2)
 for(i in 1:20000){
   percentnew[i,1]<- percent[i,1]
   sums<-sum(percent[i,2:500])
   percentnew[i,2]<-sums
 }


#Plot Number of Mutations per Individual with Selection Coef=0.001
plot(gen[,1],gen[,2],xlab="Generation",ylab="Number of Mutations per Individual", type="l", xlim=c(0,20000), ylim=c(0,thres))

#Plot the number of individuals that have mutations above the threshold vs.generation
plot(percentnew[,1],percentnew[,2]/500, type="l", xlab="Generation", ylab="% of Individuals with >4 Mutations", main="Disease Prevalance", col=c("red"), xlim=c(0,20000),ylim=c(0,1))
```
```{r}
rm(list=ls())
#Fitness Null
#Selection Coefficient=0.3
#Threshold= 9
#Recombination Rate 10^-8
thres=9
work_dir <- "~/Desktop/Research"
setwd(work_dir)

output<-read.delim("mutation10.txt", sep=" ", header=FALSE)
gen<- matrix(rep(0,40000),nrow=20000, ncol=2)

for (i in 1:20000) {
  gen[i,1]<-output[i,1]
  sum<-rowSums(output[i,2:500])
  gen[i,2]<- sum/500
}


percent<- matrix(rep(0,20000*500),nrow=20000, ncol=500)

#People with >4 mutations=1
#People with <4 mutations= 0
for (i in 1:20000){
  percent[i,1]<-output[i,1]
  
  for(t in 2:500){
   if(output[i,t] >thres)
    percent[i,t]<-1
  else
    percent[i,t]<-0
  }
}

#Sum up the number of individuals that have more than threshold value of mutations per generation
percentnew<- matrix(rep(0,40000),nrow=20000, ncol=2)
 for(i in 1:20000){
   percentnew[i,1]<- percent[i,1]
   sums<-sum(percent[i,2:500])
   percentnew[i,2]<-sums
 }


#Plot Number of Mutations per Individual with Selection Coef=0.001
plot(gen[,1],gen[,2],xlab="Generation",ylab="Number of Mutations per Individual", type="l", xlim=c(0,20000), ylim=c(0,thres))

#Plot the number of individuals that have mutations above the threshold vs.generation
plot(percentnew[,1],percentnew[,2]/500, type="l", xlab="Generation", ylab="% of Individuals with >4 Mutations", main="Disease Prevalance", col=c("red"), xlim=c(0,20000),ylim=c(0,1))
```

Decreasing Recombination Rate
```{r}
rm(list=ls())
#Fitness Null
#Selection Coefficient=0.3
#Threshold= 7
#Recombination Rate 10^-9
thres=7
work_dir <- "~/Desktop/Research"
setwd(work_dir)

output<-read.delim("mutation12.txt", sep=" ", header=FALSE)
gen<- matrix(rep(0,40000),nrow=20000, ncol=2)

for (i in 1:20000) {
  gen[i,1]<-output[i,1]
  sum<-rowSums(output[i,2:500])
  gen[i,2]<- sum/500
}


percent<- matrix(rep(0,20000*500),nrow=20000, ncol=500)

#People with >4 mutations=1
#People with <4 mutations= 0
for (i in 1:20000){
  percent[i,1]<-output[i,1]
  
  for(t in 2:500){
   if(output[i,t] >thres)
    percent[i,t]<-1
  else
    percent[i,t]<-0
  }
}

#Sum up the number of individuals that have more than threshold value of mutations per generation
percentnew<- matrix(rep(0,40000),nrow=20000, ncol=2)
 for(i in 1:20000){
   percentnew[i,1]<- percent[i,1]
   sums<-sum(percent[i,2:500])
   percentnew[i,2]<-sums
 }


#Plot Number of Mutations per Individual with Selection Coef=0.001
plot(gen[,1],gen[,2],xlab="Generation",ylab="Number of Mutations per Individual", type="l", xlim=c(0,20000), ylim=c(0,10))

#Plot the number of individuals that have mutations above the threshold vs.generation
plot(percentnew[,1],percentnew[,2]/500, type="l", xlab="Generation", ylab="% of Individuals with >7 Mutations", main="Disease Prevalance", col=c("red"), xlim=c(0,20000),ylim=c(0,1))
```



Increasing Recombination Rate
```{r}
rm(list=ls())
#Fitness Null
#Selection Coefficient=0.3
#Threshold= 9
#Recombination Rate 10^-7
thres=7
work_dir <- "~/Desktop/Research"
setwd(work_dir)

output<-read.delim("mutation13.txt", sep=" ", header=FALSE)
gen<- matrix(rep(0,40000),nrow=20000, ncol=2)

for (i in 1:20000) {
  gen[i,1]<-output[i,1]
  sum<-rowSums(output[i,2:500])
  gen[i,2]<- sum/500
}


percent<- matrix(rep(0,20000*500),nrow=20000, ncol=500)

#People with >4 mutations=1
#People with <4 mutations= 0
for (i in 1:20000){
  percent[i,1]<-output[i,1]
  
  for(t in 2:500){
   if(output[i,t] >thres)
    percent[i,t]<-1
  else
    percent[i,t]<-0
  }
}

#Sum up the number of individuals that have more than threshold value of mutations per generation
percentnew<- matrix(rep(0,40000),nrow=20000, ncol=2)
 for(i in 1:20000){
   percentnew[i,1]<- percent[i,1]
   sums<-sum(percent[i,2:500])
   percentnew[i,2]<-sums
 }


#Plot Number of Mutations per Individual with Selection Coef=0.001
plot(gen[,1],gen[,2],xlab="Generation",ylab="Number of Mutations per Individual", type="l", xlim=c(0,20000), ylim=c(0,thres))

#Plot the number of individuals that have mutations above the threshold vs.generation
plot(percentnew[,1],percentnew[,2]/500, type="l", xlab="Generation", ylab="% of Individuals with >7 Mutations", main="Disease Prevalance", col=c("red"), xlim=c(0,20000),ylim=c(0,1))
```


More fluctuations compared to the control group when you increase the recombination rate. 